Accessories dominate the costs of producing seed

### 2016-10-11 ms/Accessory/ms-supp.Rnw
adding other species to Supplementary Material

@@

>>>>

\subsection{Boronia ledifolia}

Details on parts for \emph{Boronia ledifolia} found in Table \ref{tab:parts_Boronia ledifolia}. See Fig \ref{fig:map Boronia ledifolia} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Boronia ledifolia", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(BOLE_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Boronia ledifolia}}
\label{fig:map Boronia ledifolia}
\end{figure}

@@

\subsection{Epacris microphylla}

Details on parts for \emph{Epacris microphylla} found in Table \ref{tab:parts_Epacris microphylla}. See Fig \ref{fig:map Epacris microphylla} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Epacris microphylla", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(EPMI_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Epacris microphylla}}
\label{fig:map Epacris microphylla}
\end{figure}

\subsection{Grevillea buxifolia}

Details on parts for \emph{Grevillea buxifolia} found in Table \ref{tab:parts_Grevillea buxifolia}. See Fig \ref{fig:map Grevillea buxifolia} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Grevillea buxifolia", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(GRBU_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Grevillea buxifolia}}
\label{fig:map Grevillea buxifolia}
\end{figure}

\subsection{Grevillea speciosa}

Details on parts for \emph{Grevillea speciosa} found in Table \ref{tab:parts_Grevillea speciosa}. See Fig \ref{fig:map Grevillea speciosa} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Grevillea speciosa", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(GRSP_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Grevillea speciosa}}
\label{fig:map Grevillea speciosa}
\end{figure}

\subsection{Hakea teretifolia}

Details on parts for \emph{Hakea teretifolia} found in Table \ref{tab:parts_Hakea teretifolia}. See Fig \ref{fig:map Hakea teretifolia} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Hakea teretifolia", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(HATE_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Hakea teretifolia}}
\label{fig:map Hakea teretifolia}
\end{figure}

\subsection{Hemigenia purpurea}

Details on parts for \emph{Hemigenia purpurea} found in Table \ref{tab:parts_Hemigenia purpurea}. See Fig \ref{fig:map Hemigenia purpurea} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Hemigenia purpurea", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(HEPU_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Hemigenia purpurea}}
\label{fig:map Hemigenia purpurea}
\end{figure}

\subsection{Leucopogon esquamatus}

Details on parts for \emph{Leucopogon esquamatus} found in Table \ref{tab:parts_Leucopogon esquamatus}. See Fig \ref{fig:map Leucopogon esquamatus} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Leucopogon esquamatus", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(LEES_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Leucopogon esquamatus}}
\label{fig:map Leucopogon esquamatus}
\end{figure}

\subsection{Persoonia lanceolata}

Details on parts for \emph{Persoonia lanceolata} found in Table \ref{tab:parts_Persoonia lanceolata}. See Fig \ref{fig:map Persoonia lanceolata} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Persoonia lanceolata", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(PELA_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Persoonia lanceolata}}
\label{fig:map Persoonia lanceolata}
\end{figure}

\subsection{Petrophile puchella}

Details on parts for \emph{Petrophile puchella} found in Table \ref{tab:parts_Petrophile puchella}. See Fig \ref{fig:map Petrophile puchella} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Petrophile puchella", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(PEPU_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Petrophile puchella}}
\label{fig:map Petrophile puchella}
\end{figure}

\subsection{Phyllota phyllicoides}

Details on parts for \emph{Phyllota phyllicoides} found in Table \ref{tab:parts_Phyllota phyllicoides}. See Fig \ref{fig:map Phyllota phyllicoides} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Phyllota phyllicoides", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(PHPH_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Phyllota phyllicoides}}
\label{fig:map Phyllota phyllicoides}
\end{figure}

\subsection{Pimelea linifolia}

Details on parts for \emph{Pimelea linifolia} found in Table \ref{tab:parts_Pimelea linifolia}. See Fig \ref{fig:map Pimelea linifolia} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Pimelea linifolia", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(PILI_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Pimelea linifolia}}
\label{fig:map Pimelea linifolia}
\end{figure}

\subsection{Pultanaea tuberculata}

Details on parts for \emph{Pultanaea tuberculata} found in Table \ref{tab:parts_Pultanaea tuberculata}. See Fig \ref{fig:map Pultanaea tuberculata} for a plot.

<<echo=FALSE,results='asis'>>=
  print_table_species("Pultanaea tuberculata", flowering_parts)
@

  \begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(PUTU_GraphMaps$graph)
@
  \caption{Map of parts for \emph{Pultanaea tuberculata}}
\label{fig:map Pultanaea tuberculata}
\end{figure}
